19Q2

### 2019-12-16 19Q2.Rmd
small edits during manuscript discussion w/ Daniel

@@

```{r spear_calc_lin, eval=FALSE}
# Ran on 12/3
crispr_cn_res_lin <- MakeSpearmanCorrDF(dataset = "CRISPR", df = crispr, metric = "CN", lineage = TRUE)
ccle_cn_res_lin <- MakeSpearmanCorrDF(dataset = "CCLE", df = ccle, metric = "CN", lineage = TRUE)
ctrp_cn_res_lin <- MakeSpearmanCorrDF(dataset = "CTRP", df = ctrp, metric = "CN", lineage = TRUE)
gdsc_cn_res_lin <- MakeSpearmanCorrDF(dataset = "GDSC", df = gdsc, metric = "CN", lineage = TRUE)
cn_cor_lin <- rbind(crispr_cn_res_lin, ccle_cn_res_lin, ctrp_cn_res_lin, gdsc_cn_res_lin) %>% filter(CN_p_log10 != Inf)
saveRDS(cn_cor_lin, "./data_munging/rds/cn_cor_lineage.rds")

@@

>>>>

```{r fig.width=10}
ggplot(data = ccle_fus) + 
  geom_boxplot(aes(x = disease, y = Score)) +

```

@@

**12/16 FIX THIS **
```{r spear_calc_lin, eval=FALSE}
# Ran on 12/3
crispr_cn_res_lin <- MakeSpearmanCorrDF(dataset = "CRISPR", df = crispr, metric = "CN", lineage = TRUE)
ccle_cn_res_lin <- MakeSpearmanCorrDF(dataset = "CCLE", df = ccle, metric = "CN", lineage = TRUE)
ctrp_cn_res_lin <- MakeSpearmanCorrDF(dataset = "CTRP", df = ctrp, metric = "CN", lineage = TRUE)
gdsc_cn_res_lin <- MakeSpearmanCorrDF(dataset = "GDSC", df = gdsc, metric = "CN", lineage = TRUE)
cn_cor_lin <- rbind(crispr_cn_res_lin, ccle_cn_res_lin, ctrp_cn_res_lin, gdsc_cn_res_lin) %>% filter(CN_p_log10 != Inf)
saveRDS(cn_cor_lin, "./data_munging/rds/cn_cor_lineage.rds")

@@

```{r}
cn_cor_lin <- readRDS("./data_munging/rds/cn_cor_lineage.rds")
ge_cor_lin <- readRDS("./data_munging/rds/ge_cor_lineage.rds")
```
